\begin{acknowledgements}
  % General intro sentence
  This thesis is for me, as perhaps for many, the fulfilment of a childhood
  goal. I have not arrived here alone, and there are many people I would like to
  thank.

  % Ray
  First and foremost to my supervisor Raymond Volkas, to whom I owe a great debt
  of gratitude: thank you for accepting me as your student under what were
  certainly unorthodox circumstances; for all of the opportunities you offered
  to me in the course of the PhD, especially for work and travel; and for your
  mentoring in both my personal and professional life. I am deeply grateful to
  have had the opportunity to study under such a sharp physicist, and such an
  encouraging friend.

  % Panel
  To the other members of my advisory panel, Nicole Bell and Jeff McCallum,
  thank you for your encouragement and support.

  % Collaborators
  I have been very fortunate to have worked with many dedicated and intelligent
  collaborators over the course of my doctorate. To Innes Bigaran, Yi Cai, Noel
  Dawe, Matthew Dolan, Robert Foot, Ayodele Ore and Iulia Popa-Mateiu, working and learning
  from you has been a pleasure and an invaluable part of my PhD experience.
  Special mention must go to Matthew Dolan: thank you for your patience and
  mentoring.

  % Office mates
  Discussions and interactions with postdocs and other students have helped me
  greatly in my time as a student. In particular I would like to thank my
  doctoral contemporaries Leon Friedrich and Tomasz Dutka, for whom, as with me,
  physics is as much a passion as it is work. I would also like to thank the
  remaining students with whom I had the pleasure of sharing the theory PhD
  office at one point or another: Jackson Clarke, Peter Cox, Joshua Ellis,
  Rebecca Leane, Nick Leerdam, Stephen Lonsdale and Isaac Sanderson.

  % Friends
  The encouragement, interest and support of my friends outside of the David
  Caro building have been a constant source of motivation for me. I thank in
  particular Dean, Mariah, Mark, Tom and Yianni for their friendship.

  % Parents and family
  Of course, this work would not have been possible without the constant love
  and support of my family. I thank my sister for her readiness to listen, and for periodically reminding me to take a break from work.  I am indebted to my parents for encouraging me to pursue my interests, and their unconditional and ready
  assistance through every step of the journey. My curiosity about the world did
  not emerge \textit{in vacuo}, and I have my parents and grandparents to thank
  for instilling in me a love of learning and science. Thank you for these
  priceless gifts. My time as a PhD student also saw the birth of four children into my life. Thank you to Mary, George, George and Johnny, who have made these years immeasurably more enjoyable.

  % Sabrina
  Finally to Sabrina, thank you for your understanding, encouragement and
  patience. I am deeply grateful to have had you by my side for the completion
  of my doctorate. Thank you for supporting me and keeping me sane in what is
  all too often a consuming line of work.
\end{acknowledgements}
