\begin{preface}
  Particle physics currently finds itself in a strange or exciting place,
  depending on who you ask. The discovery of a Higgs-like boson at close to
  $\SI{125}{\GeV}$ has meant both the completion of the Standard Model (SM), and
  the end of clear signs of new particles at the electroweak scale. Although the
  Large Hadron Collider (LHC) will continue to collect data well into the next
  few decades, the mass reach will not increase significantly. The community
  waits for a new machine, for which there are many candidates and promises,
  that will continue to push the energy frontier and test theories addressing
  the many shortcomings of the SM. Time frames for many of these see data taking
  beginning at the end of my career. If progress is driven by experiment, where
  do we go from here?

  Thankfully, there are already clear signs of new physics in the neutrino
  sector. The observation of neutrino oscillations, and therefore neutrino
  masses, is by far the strongest terrestrial evidence demanding an extension of
  the SM. It is no surprise that a full understanding of the neutrinos has
  alluded us so far; they are, with the possible exception of the Higgs boson,
  the most elusive particles currently under laboratory scrutiny. As we move
  into an era of precision neutrino measurements, now is the right time to take
  stock of the phenomenologically viable and economic models that explain the
  pattern of neutrino masses and mixings observed. Armed with the list of
  possible mechanisms, we can make progress in probing those that are testable
  and, given that these models are falsified, build circumstantial evidence in
  favour of those that are not.

  Even on the collider front, it is unclear yet that the LHC has left us with
  the so-called `nightmare scenario' of a lonely Higgs. Perhaps unexpectedly,
  the most interesting signs of new physics from CERN have come from the
  LHC\textit{b} experiment. The now famous `flavour anomalies' are a collection
  of theoretically consistent anomalous measurements indicating a departure from
  the lepton-flavour universality present in the SM. Are these related to the
  growing evidence for deviations in leptonic anomalous magnetic moments? Might
  they be clues to a deeper theory of flavour and mass? The Belle II experiment
  has only just begun taking data, and we wait eagerly for what it has to say on
  these matters. LHC\textit{b} too will continue to improve its measurements
  with more collisions; if the anomalies persist, these will be undeniable
  evidence of physics beyond the SM accessible to the next generation of hadron
  colliders.

  These measurements are tantalising because of their consistency and breadth,
  but it would not be the first time that physicists have been lead astray,
  should they disappear with more statistics. Even so, what is perhaps the
  central result of my doctoral work will remain unchanged: that deviations from
  lepton-flavour universality in four-fermion operators may be intimately
  connected to mass generation in the neutrino sector.

  This idea is developed over the six chapters of this thesis, four of which are
  based on publications and preprints written in collaboration. These are
  summarised below with a statement of contribution and the publication status
  of the papers on which the chapters are based.
  \begin{itemize}
    \item Chapter~\ref{chapter:introduction} is an original introduction and
          literature review outlining the background necessary to understand the
          remaining chapters.
    \item Chapter~\ref{chapter:mv-models} is based on the preprint `Exploding
          operators for Majorana neutrino masses and beyond,' written in
          collaboration with Raymond R. Volkas~\cite{Gargalionis:2020xvt}. The
          paper has recently been accepted for publication in JHEP. The
          calculations, analysis and technical writing in this chapter are
          largely my own. The ideas motivating the work were developed with
          Raymond R. Volkas.
    \item Chapter~\ref{chapter:the-one-lq} is based on the publication
          `Reconsidering the One Leptoquark solution: flavor anomalies and
          neutrino mass,' written in collaboration with Yi Cai, Michael A.
          Schmidt and Raymond R. Volkas~\cite{Cai:2017wry}, and `A near-minimal
          leptoquark model for reconciling flavour anomalies and generating
          radiative neutrino masses,' written with Innes Bigaran and Raymond R.
          Volkas~\cite{Bigaran:2019bqv}. The calculations, analysis and
          technical writing in this chapter are largely my own. The motivation
          for this detailed phenomenological analysis of the $S_{1}$ leptoquark
          model stemmed from an idea of Michael A. Schmidt of embedding it into
          a model of radiative neutrino mass.
    \item Chapter~\ref{chapter:neutrino-mass-and-flavour-anomalies} is based on
          the publications `Reconsidering the One Leptoquark solution: flavor
          anomalies and neutrino mass,' written in collaboration with Yi Cai,
          Michael A. Schmidt and Raymond R. Volkas~\cite{Cai:2017wry}, and `A
          near-minimal leptoquark model for reconciling flavour anomalies and
          generating radiative neutrino masses,' written with Innes Bigaran and
          Raymond R. Volkas~\cite{Bigaran:2019bqv}. The content of all sections
          except Sec.~\ref{sec:ch4-rad-models-flav-anomalies} has been published
          in one of the aforementioned publications.
          Sec.~\ref{sec:ch4-non-minimal} contains work performed by
          collaborators, specifically the development of the model and the
          underlying computational machinery discussed in
          Sec.~\ref{sec:ch4-innes-constraints}. The remaining technical work is
          largely my own, and the exposition of the model presented here is also
          my own. The motivation for this work followed from the limited success
          of the $S_{1}$ leptoquark scenario in both the neutrino-mass setting
          and as a combined explanation of the flavour anomalies. It was the
          idea of Raymond R. Volkas to combine the two dimension-seven
          completions containing $S_{3}$ and $S_{1}$ into the non-minimal model
          studied in detail in Sec.~\ref{sec:ch4-non-minimal}.
    \item Chapter~\ref{chapter:quirk} is based on the publication `Explaining
          the \SI{750}{\GeV} diphoton excess with a colored scalar charged under
          a new confining gauge interaction,' written in collaboration with
          Robert Foot. The calculation of the production cross section was my
          own work, otherwise the work was mostly completed by Robert Foot.
    \item Chapter~\ref{chapter:conclusions} provides some concluding comments of
          my own about the thesis as a whole.
    \end{itemize}

\end{preface}
